How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-16 docs/PhysicsPaper/StokesErosion.tex
NM

The effects of flow-induced erosion are visible across a range of scales in the natural world, from massive geological structures \cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns \cite{berhanu2012shape, bertagni2021hydrodynamic}, and down to the granular constituents comprising porous media \cite{zareei2022temporal}. Porous media encountered in natural settings typically exhibit {\em anisotropic} material properties,

>>>>

The effects of flow-induced erosion are visible across a range of scales in the natural world, from massive geological structures \cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns \cite{berhanu2012shape, bertagni2021hydrodynamic}, and down to the granular constituents of porous media \cite{zareei2022temporal}. The porous media encountered in nature typically exhibit material {\em anisotropy} in that they permit seepage flow in one direction more easily than in others. Typically, materials can be more permeable to flow in the longitudinal direction by a factor of 5-20 \cite{bear1988dynamics, anderson2015applied}.
